One-at-a-time Parameter Perturbation Ensemble of the Community Land Model, version 5.1

### 2025-04-09 ms/ms.tex
new references

Understanding the range of outcomes arising from the many plausible parameter combinations is a critical step in robust uncertainty quantification. Parameter sensitivity tests can be used to gauge parametric uncertainty, and a collection of systematic parameter sensitivity tests across multiple parameters is often termed a Perturbed Parameter Ensemble (PPE, also referred to as Perturbed Physics Ensemble), with examples in the coupled \cite{murphy2004} and land-only contexts \add{zqzbaker2022} \cite{dagon2020,mcneall2024}. 
One important application of PPEs has been assessing uncertainty in climate model projections \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
Beyond uncertainty quantification, PPEs also form a basis for automated model calibration through various approaches like history matching, \add{which does not require assumptions regarding parameter distributions} \cite{williamson2013,williamson2017,hourdin2020,couvreux2021,mcneall2024}, or Bayesian methods \add{zqz zeihn2012,fer2018} \cite{cleary2021}, \add{or using genetic algorithms zqz bastrikov2018}.
Several promising avenues for model calibration are in development \cite{pinnington2020,cleary2021,alonso-gonzalez2022}, many of which require the construction of large PPEs \cite{qian2018}.
In a more general sense, PPEs yield a robust knowledge basis for understanding and working with a given climate model. This can aid in introducing new users to the model, or to help steer and facilitate model development.

@@

The second challenge involved defining a perturbation range for each parameter. We solicited expert judgment to set a minimum and maximum reasonable value for each parameter. In some cases, literature values were explicitly used (e.g. for the slope parameter of the stomatal conductance model, `medlynslope', \citeA{lin2015}), but the most common range was $\pm20\%$. It is exceedingly difficult to set parameter ranges that sample comparable probability density, even in a univariate experiment, like this one. The number of parameters is large, with many lacking sufficient empirical backing for robust range evaluation. Defining appropriate ranges for the full suite of land model parameters is a major activity of the scientific subdomains that comprise land models \cite{kattge2020}. Even with parameters that have an empirical basis from field studies, uncertainty quantification is difficult due to the scale mismatch between site-level observations and land model grid cells zqz \cite{liu2021}. As such, we cannot claim that the parameters are equivalently sampled, whereby parameter effects and parameter rankings could be subject to sampling asymmetries.

>>>>

Understanding the range of outcomes arising from the many plausible parameter combinations is a critical step in robust uncertainty quantification. Parameter sensitivity tests can be used to gauge parametric uncertainty, and a collection of systematic parameter sensitivity tests across multiple parameters is often termed a Perturbed Parameter Ensemble (PPE, also referred to as Perturbed Physics Ensemble), with examples in the coupled \cite{murphy2004} and land-only contexts \add{new citation} \cite{dagon2020,baker2022,mcneall2024}. 
One important application of PPEs has been assessing uncertainty in climate model projections \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
Beyond uncertainty quantification, PPEs also form a basis for automated model calibration through various approaches like history matching, \add{which does not require assumptions regarding parameter distributions} \cite{williamson2013,williamson2017,hourdin2020,couvreux2021,mcneall2024}, or Bayesian methods \add{new citations} \cite{ziehn2012,fer2018,cleary2021}, \add{or using genetic algorithms} \cite{bastrikov2018}.
Several promising avenues for model calibration are in development \cite{pinnington2020,cleary2021,alonso-gonzalez2022}, many of which require the construction of large PPEs \cite{qian2018}.
In a more general sense, PPEs yield a robust knowledge basis for understanding and working with a given climate model. This can aid in introducing new users to the model, or to help steer and facilitate model development.

@@

The second challenge involved defining a perturbation range for each parameter. We solicited expert judgment to set a minimum and maximum reasonable value for each parameter. In some cases, literature values were explicitly used (e.g. for the slope parameter of the stomatal conductance model, `medlynslope', \citeA{lin2015}), but the most common range was $\pm20\%$. It is exceedingly difficult to set parameter ranges that sample comparable probability density, even in a univariate experiment, like this one. The number of parameters is large, with many lacking sufficient empirical backing for robust range evaluation. Defining appropriate ranges for the full suite of land model parameters is a major activity of the scientific subdomains that comprise land models \cite{kattge2020}. Even with parameters that have an empirical basis from field studies, uncertainty quantification is difficult due to the scale mismatch between site-level observations and land model grid cells \cite{liu2021}. As such, we cannot claim that the parameters are equivalently sampled, whereby parameter effects and parameter rankings could be subject to sampling asymmetries.
